A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

PCA, SVD and POD are closely related. In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as the Karhunen-Loeve Transformation (KLT) \cite{Jafarpour_2009}.

A lot of the recent research in the field of petroleum engineering field which use these techniques, focus on the problem of history matching \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}. History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

>>>>

PCA, SVD and POD are closely related. In the petroleum engineering community where these techniques are used for reservoir characterization, they are sometimes used interchangable, and are normally referred to as Karhunen-Loeve Transformations (KLT) \cite{Jafarpour_2009}.

A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}). History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
